Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2020-06-04 doc/supp.tex
final final

\begin{figure}[!h]
\includegraphics[width=\textwidth]{../fig/cmp_reproductive_underreport.pdf}
\caption{\textbf{Comparison of estimates of reproductive number based on various methods.}
This figure matches Fig. 4 in the main text.
We assume that infected indidividuals have 30\% binomial probability of reporting their generation intervals (time between their infection and the infection of their infectors) when we apply population- and individual-based methods to estimate \Rini;
under-reporting of generation intervals still give unbiased estimates of \Rini.
All other parameters and estimates are the same as in Fig. 4 in the main text.
}
\label{fig:cmpsmall}
\end{figure}

>>>>

\begin{figure}[!h]
\includegraphics[width=\textwidth]{../fig/cmp_reproductive_underreport.pdf}
\caption{\textbf{Comparison of estimates of reproductive number based on various methods.}
This figure matches Fig. 4 in the main text.
We assume that infected indidividuals have 30\% binomial probability of reporting their generation intervals (time between their infection and the infection of their infectors) when we apply population- and individual-based methods to estimate \Rini.
We still obtain unbiased estimates of \Rini when generation intervals are under-reported.
All other parameters and \Rini estimates (boxplots) are the same as in Fig. 4 in the main text.
}
\label{fig:cmpsmall}
\end{figure}
